Dynein project log

### 2016-08-02 thesis_stuff/thesis_stuff.tex
Add beginning of CLT derivation.

>>>>

\section{Background of Correlation function}
This is based on the Autocorrelation procedure (see Convolution on Wikipedia).
In our correlation function code, we take the autocorrelation function of our
potential and time-translate it to get the time at which there is zero correlation
between the functions. Flesh this out sometime!\\

\section{CLT (and/or Brownian distribution is Gaussian?) Derivation}
Here we show that, given an initial PDF as a delta function $P(t_0,x) = \delta(x)$
and any transition likelihood $W(s)$ for some step size s and 1 timestep, P
eventually evolves into a Gaussian function.\\

We use a discrete time, continuous position model:\\

\begin{align}
  P(t_0+1,x') &= \int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx\\
\end{align}

This matches the form of a convolution integral:

\begin{align*}
  (P*W)(x') &= \int_{-\infty}^{\infty}P(t_0,x)W(x'-x)dx\\
\end{align*}

By the Convolution Theorem (prove?) we can simplify the above expression:

\begin{align}
  F{P(t_0+1,x')} &= F{\int_{-\infty}^{\infty}W(x'-x)P(t_0,x)dx}\\
  \tilde{P(t_0+1,k)} &= N\tilde{W(k)}\tilde{P(t_0,k)}\\
\end{align}

We now let our initial time $t_0$ be zero and note that, because
$W_n(\delta x) = W(\delta x)^n$, we can simplify our expression to:

\begin{align}
  \tilde{P(n,k)} &= N\tilde{W(k)}^n\tilde{P(t_0,k)}\\
\end{align}

We then take the Inverse Fourier Transform of this expression, yielding:

\begin{align}
  P(n,x) &= \int_{-\infty}^{\infty}\tilde{P(n,k)}e^{2\pi ikx}dk
  = N\int_{-\infty}^{\infty}\tilde{W(k)}^n\tilde{P(t_0,k)}e^{2\pi ikx}dk\\
\end{align}

Since $P(0,x)$ is a delta function, we know that $\tilde{P}(0,x) = 1$, so:

\begin{align}
  P(n,x) &=  N\int_{-\infty}^{\infty}\tilde{W(k)}^ne^{2\pi ikx}dk\\
\end{align}
